\documentclass[letterpaper,11pt]{article}

% Choose bibliography style for formatting list of publications
\usepackage[style=ieee,url=false,doi=false,maxbibnames=99,sorting=ydnt,dashed=false]{biblatex}
\bibliography{papers}

% Choose theme, e.g. black, RedViolet, ForestGreen, MidnightBlue

\def\theme{Mycolor}

% More predefined colors can be found in 
% https://en.wikibooks.org/wiki/LaTeX/Colors
% Example photograph taken from Wikimedia Commons
% https://commons.wikimedia.org/wiki/File:Kiara_Krit_passport.jpg

\usepackage{simplecv}
\usepackage{changepage}


\boldname{Corbin}{Nicholas}{A.}

\begin{document}
\newcommand{\makeauthorbold}[1]{%
  \DeclareNameFormat{author}{%
    \ifthenelse{\value{listcount}=1}
    {%
      {\expandafter\ifstrequal\expandafter{\namepartfamily}{#1}{\mkbibbold{\namepartfamily\addcomma\addspace \namepartgiveni}}{\namepartfamily\addcomma\addspace \namepartgiveni}}
      %
    }{\ifnumless{\value{listcount}}{\value{liststop}}
      {\expandafter\ifstrequal\expandafter{\namepartfamily}{#1}{\mkbibbold{\addcomma\addspace \namepartfamily\addcomma\addspace \namepartgiveni}}{\addcomma\addspace \namepartfamily\addcomma\addspace \namepartgiveni}}
      {\expandafter\ifstrequal\expandafter{\namepartfamily}{#1}{\mkbibbold{\addcomma\addspace \namepartfamily\addcomma\addspace \namepartgiveni\addcomma\isdot}}{\addcomma\addspace \namepartfamily\addcomma\addspace \namepartgiveni\addcomma\isdot}}%
    }
    \ifthenelse{\value{listcount}<\value{liststop}}
    {\addcomma\space}
  }
}
\makeauthorbold{Corbin}
% Heading
\headinginline{Nicholas Corbin}{
  Email: \email{ncorbin@ucsd.edu} \\
  % LinkedIn: \linkedin{nick-corbin} \\
  Website: cnick1.github.io\\
  % GitHub: \github{cnick1}
}


% Page One
\section{Education}

\outerlist{

  \entrybig
  {\textbf{University of California San Diego}}{La Jolla, CA}
  {Ph. \hspace{-.4em}D. in Mechanical and Aerospace Engineering, GPA: 3.95/4.00}{Fall 2021\textendash  Present}
  {\small Specialization in Linear and Optimal Control}

  \entrybig
  {\textbf{Virginia Tech}}{Blacksburg, VA}
  {M.S. in Engineering Mechanics, GPA: 3.92/4.00}{2019\textendash  2021}
  {\small Thesis: \textit{Dispersion Curve Estimation for Longitudinal Rail Stress Measurement}}
  \entrybig
  {\textbf{Virginia Tech}}{Blacksburg, VA}
  {B.S. in Engineering Science and Mechanics, GPA: 3.93/4.00}{2015\textendash  2019}
  {\small Minor in Mathematics}
  % Major GPA 3.88

}



% Can instead manually enter publications as shown:
\section{Publications}
\orderedouterlist{
  \entry{\textbf{N. Corbin,} B. Kramer, "Computing solutions to the polynomial-polynomial-regulator problem", Submitted to CDC, 2024.}
  \entry{\textbf{N. Corbin,} B. Kramer, "Scalable computation of $\mathcal{H}_\infty$ energy functions for polynomial drift nonlinear systems", Accepted for publication at ACC, 2024.}
  \entry{\textbf{N. Corbin,} B. Kramer, "Scalable computation of $\mathcal{H}_\infty$ energy functions for polynomial control-affine systems", Submitted, 2023.}
  \entry{\textbf{N. Corbin,} M. Albakri, P. Tarazaga, "Reference-free longitudinal rail stress and neutral temperature measurement utilizing multidirectional elastic waves", Tech. Rep. submitted to the Federal Railroad Administration, 2021.}
  \entry{N. P. Bende, T. Yu, \textbf{N. Corbin,} M. A. Dias, C. D. Santangelo, J. A. Hanna, R. C. Hayward, "Overcurvature induced multistability of linked conical frusta: How a ‘bendy straw’ holds its shape", Soft Matter, vol. 14, no. 42, pp. 8636–8642, 2018.}
  \entry{\textbf{N. Corbin,} J. A. Hanna, W. R. Royston, H. Singh, R. B. Warner, "Impact-induced acceleration by obstacles", New Journal of Physics, vol. 20, no. 5, p. 053031, May 2018.}
}

% \begin{adjustwidth}{-23.5pt}{-5pt}

% Can instead manually enter publications as shown:
\section{Conference Presentations}
\orderedouterlist{
  % \entry{\textbf{N. Corbin,} B. Kramer, "Computing solutions to the polynomial-polynomial-regulator problem", \textit{Conference on Decision and Control (CDC)}, December 2024.}

  % \entry{\textbf{N. Corbin,} B. Kramer, "Scalable computation of $\mathcal{H}_\infty$ energy functions for polynomial control-affine systems", \textit{American Control Conference (ACC)}, July 2024.}

  \entry{\textbf{N. Corbin,} B. Kramer, "Nonlinear balancing for quadratic-bilinear systems", \textit{SIAM Conference on Control and Its Applications}, July 2023.}

  \entry{\textbf{N. Corbin,} B. Kramer, "Nonlinear balancing for quadratic-bilinear systems", \textit{Nonlinear Model Reduction for Control Conference at Virginia Tech}, May 2023.}

  \entry{\textbf{N. Corbin,} M. Albakri, and P. Tarazaga, "Numerical evaluation of a low-frequency acoustoelastic technique for longitudinal rail stress measurement", \textit{38\textsuperscript{th} International Modal Analysis Conference (IMAC)}, February 2020.}

  \entry{K. Mize, \textbf{N. Corbin,} and P. Tarazaga, "A mass-normalized projection approach to component testing", \textit{90\textsuperscript{th} Shock and Vibrations Exchange (SAVE)}, November 2019.}

  \entry{\textbf{N. A. Corbin}, J. A. Hanna, W. R. Royston, H. Singh, and R. B. Warner, ``V0022: Chain coiling and impinging'', \textit{Gallery of Fluid Motion, 70\textsuperscript{th} Annual Meeting of the APS Division of Fluid Dynamics}, November 2017.}
}


\section{Industry Experience}

\outerlist{
  \entrybig
  {\textbf{Pratt and Whitney}}{East Hartford, CT}
  {Core Structures Intern}{May 2018\textendash  August 2018}
  {Mentor: Ben Hall}
  \innerlist{
    \entry{Nonlinear vibration analysis, computational fluid dynamics, and crack propogation analysis for aircraft engines.}
  }

}

\section{Design Teams}

\outerlist{

  \entrybig
  {\textbf{ESM Rocketry Senior Design,} NASA University Student Launch Initiative 2019 }{Blacksburg, VA}
  {Payload Subteam Lead and Document Editor}{January 2018\textendash  May 2019}
  \innerlist{
    \entry{Co-founded and helped lead a team of 7 competing in NASA USLI competition. Designed \& built a Level 2 high power rocket and deployable autonomous UAV payload system. }
  }

  \entrybig
  {\textbf{RockSat-X @ Virginia Tech}}{Blacksburg, VA}
  {Team Lead and Mechanical Subteam Lead}{September 2017\textendash  August 2018}
  \innerlist{
    \entry{Led team of 15 in the design and manufacturing of a 15-pound sounding rocket scientific payload for launch with apogee of 90 miles from NASA Wallops Flight Facility in August each year. Payload designs included software-defined radio for tracking boats and planes from space and FlatSat small form factor deployable experiment platform.}
  }

}

\section{Mentorship and Outreach}

\outerlist{
  \entrybig
  {\textbf{Undergraduate research mentor}}{La Jolla, CA and Blacksburg, VA}
  {Student mentor}{2019, 2020, 2022}
  \innerlist{
    \entry{Have mentored four undergraduate researchers: Kam Mize and Tylor Pugh under Dr. Tarazaga at Virginia Tech, and  Antoinette Gautier and Jason Stanley under Dr. Kramer at UCSD. }
  }
  \entrybig
  {\textbf{Virginia Tech ESM senior design advisor}}{Blacksburg, VA}
  {Team sponsor/advisor}{August 2020\textendash  May 2021}
  \innerlist{
    \entry{Sponsored and mentored a senior design team through UpStream Services LLC startup that I co-founded to develop innovative waste-measurement device. }
  }
  \entrybig
  {\textbf{Rocketry outreach}}{New River Valley, VA}
  {Floyd Elementary School Outreach}{February 2019}
  \innerlist{
    \entry{Organized day-long outreach event with Floyd Elementary School to expose 251 students (grades 1-5) to STEM and rocketry through short lessons and hands-on ``bubble rockets'' activity. }
  }

  \vspace{-.5cm}
  \entrybig
  {}{}
  {Blacksburg High School FlatSat Project}{January 2018\textendash  August 2018}
  \innerlist{
    \entry{Under my leadership, the Rocksat-X @ Virginia Tech team designed and built a deployment, power, and telemetry platform for small deployable experiments. We then partnered with Blacksburg High School to have students build three experiments of their choice, which ultimately were 1) a reaction-control experiment to try to control the orientation of the deployables, 2) a Geiger counter to measure radiation in the thermosphere, and 3) a spectrometry experiment to measure the makeup of the thermosphere.}
  }
}

\section{Fellowships and Awards}
\vspace*{-0.4cm}
\begin{multicols}{2}
  \begin{itemize}[leftmargin=*, noitemsep]
    \item UCSD Powell Fellowship (2021)
    \item Liviu Librescu Memorial Fellowship (2020)
    \item NSF GRFP Honorable Mention (2020)
    \item James H. Sword Award (2019)
  \end{itemize}
\end{multicols}




% \end{adjustwidth}

\end{document}
