% \vspace{-.5cm}
% \nocite{*}
% % \printbibliography[title=Publications]
%\oddsidemargin = -9pt

% Can instead manually enter publications as shown:
\section{Publications}
\orderedouterlist{
    \entry{\textbf{N. Corbin,} B. Kramer, \href{https://doi.org/10.1109/TAC.2024.3494472}{``Scalable computation of $\mathcal{H}_\infty$ energy functions for polynomial control-affine systems''}, IEEE Transactions on Automatic Control, 2024.}
    \entry{\textbf{N. Corbin,} A. Sarkar, J. Scherpen, and B. Kramer, \href{https://arxiv.org/abs/2410.22435}{``Scalable computation of input-normal/output-diagonal balanced realization for control-affine polynomial systems''}, submitted 2024.}
    \entry{\textbf{N. Corbin,} B. Kramer, "Computing solutions to the polynomial-polynomial regulator problem", in 2024 63rd IEEE Conference on Decision and Control, Dec. 2024.}
    \entry{\textbf{N. Corbin,} B. Kramer, \href{https://doi.org/10.23919/acc60939.2024.10644363}{``Scalable computation of $\mathcal{H}_\infty$ energy functions for polynomial drift nonlinear systems''}, in 2024 American Control Conference, Jul. 2024, pp. 2506–2511.}
    \entry{\textbf{N. Corbin,} M. Albakri, P. Tarazaga, ``Reference-free longitudinal rail stress and neutral temperature measurement utilizing multidirectional elastic waves'', Tech. Rep. submitted to the Federal Railroad Administration, 2021.}
    \entry{N. P. Bende, T. Yu, \textbf{N. Corbin,} M. A. Dias, C. D. Santangelo, J. A. Hanna, R. C. Hayward, \href{https://doi.org/10.1039/C8SM01355A}{``Overcurvature induced multistability of linked conical frusta: How a ‘bendy straw’ holds its shape''}, Soft Matter, vol. 14, no. 42, pp. 8636–8642, 2018.}
    \entry{\textbf{N. Corbin,} J. A. Hanna, W. R. Royston, H. Singh, R. B. Warner, \href{https://doi.org/10.1088/1367-2630/aac151}{``Impact-induced acceleration by obstacles''}, New Journal of Physics, vol. 20, no. 5, p. 053031, May 2018.}
}
