\section{Research and Work Experience}

\outerlist{

	\entrybig
	{\textbf{Kramer Research Group}}{La Jolla, CA}
	{Graduate Research Assistant}{September 2021\textendash  Present}
	{Advisor: Dr. Boris Kramer}
	% \innerlist{
	% 	\entry{Dispersive wave propagation: \textcolor{color-detail}{researching structural health monitoring (SHM) technique using low-frequency dispersive flexural waves for non-destructive stress measurement for the Federal Railroad Administration.}}
	% 	\entry{Data-driven modeling: \textcolor{color-detail}{researching rational transfer function fitting for characterizing dispersion information and boundary conditions from modal test data.}}
	% }

	\entrybig
	{\textbf{Vibrations, Adaptive Structures, and Testing Lab (VAST)}}{Blacksburg, VA}
	{Graduate Research Assistant}{May 2019\textendash  July 2021}
	{Advisor: Dr. Pablo Tarazaga}
	\innerlist{
		\entry{Dispersive wave propagation: \textcolor{color-detail}{researched structural health monitoring (SHM) technique using low-frequency dispersive flexural waves for non-destructive stress measurement for the Federal Railroad Administration.}}
		\entry{Data-driven modeling: \textcolor{color-detail}{investigated rational transfer function fitting for characterizing dispersion information and boundary conditions from modal test data.}}
	}

	\entrybig
	{\textbf{Pratt and Whitney}}{East Hartford, CT}
	{Core Structures Intern}{May 2018\textendash  August 2018}
	{Mentor: Ben Hall}
	\innerlist{
		\entry{Sub-idle modal parameter estimation: \textcolor{color-detail}{analyzed nonlinear vibrations using test data from airfoils in gas-turbine engines during startup to extract sub-idle modal parameters using Python.}}
		\entry{CFD validation streamlining: \textcolor{color-detail}{created scripts for automatic CFD vibratory stress prediction validation to accelerate transition of software from experimental to production usage.}}
	}

	\entrybig
	{\textbf{Mechanics of Thin Structures Group}}{Blacksburg, VA}
	{Undergraduate Research Assistant}{January 2016\textendash  August 2018}
	{Advisor: Dr. James Hanna}
	\innerlist{
		\entry{Ran experiments using tools including high speed imagery, particle image velocimetry, 3D-printing, and processed data using Matlab, Mathematica, and FFMPEG.}
	}
}